---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# zewplot

<!-- badges: start -->
<!-- badges: end -->

The package `zewplot` implements the function `zew_plotstyle()`

## Installation

It is necessary to install the `devtools` package.
Then, `zewplot` can be installed from the GitHub repository:

``` r
install.packages('devtools')
library(devtools)
install_github('benediktstelter/zewplot')
```

## Example


```{r example, echo=TRUE, warning=FALSE, message=FALSE}
library(tidyverse)
library(zewplot)
# Data preparation
df <- economics %>%
  select(date, psavert, uempmed) %>%
  gather(key = "variable", value = "value", -date)
#Plotting using zew_plotstyle
example_plot <- ggplot(df, aes(x = date, y = value)) + 
  geom_line(aes(color = variable), size = 1) +
  scale_color_manual(values = c("#b4be28", "#527ca4")) +
  zew_plotstyle()

```



```{r fig.asp = 0.7, fig.width = 5, echo=FALSE, warning=FALSE}
example_plot
```

It is also possible to select a custom font and change the font size (default font size is 12) through the arguments `font` and `font_size`:

```{r example2, echo=TRUE, warning=FALSE, message=FALSE}
#Load custom font (e.g. Latin Modern Roman 10: "LaTeX Font")
library(showtext)
font_add(family = "Latin Modern Roman 10", regular = "example/lmroman10-regular-webfont.ttf")
showtext_auto()
#Plotting using zew_plotstyle with custom font and custom font size
example_plot2 <- ggplot(df, aes(x = date, y = value)) + 
  geom_line(aes(color = variable), size = 1) +
  scale_color_manual(values = c("#b4be28", "#527ca4")) +
  zew_plotstyle(font = "Latin Modern Roman 10", font_size = 8)

```

```{r fig.asp = 0.7, fig.width = 5, echo=FALSE, warning=FALSE}
example_plot2
```

As a third argument, it is possible to flip the design of the x-axis and y-axis using `flipped = TRUE` (default setting is `flipped = FALSE`), which might be useful in certain applications (not in this example though):


```{r example3, echo=TRUE, warning=FALSE, message=FALSE}
#Plotting using zew_plotstyle with custom font and custom font size as well as flipped axis design
example_plot3 <- ggplot(df, aes(x = date, y = value)) + 
  geom_line(aes(color = variable), size = 1) +
  scale_color_manual(values = c("#b4be28", "#527ca4")) +
  zew_plotstyle(font = "Latin Modern Roman 10", font_size = 8, flipped = TRUE)

```

```{r fig.asp = 0.7, fig.width = 5, echo=FALSE, warning=FALSE}
example_plot3
```
